Global Reach or Out of Reach

### 2019-05-11 Paper_markdown.Rmd
Working

@@

##Analysis

The plot of the first set of results shows the

```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}

dwplot(list(MID_BI_Log, Force_BI_Log),
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))

@@

```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}

dwplot(list(MID_BI_Log, Force_BI_Log),
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))

>>>>

#Full Models
  #Logistic regression
MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
summary(MID_Full_Log) 
dwplot(MID_Full_Log)

MID_Full_Log <- glm(Mid ~ US_Tonnage + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
summary(MID_Full_Log)

ODDS_MID_FULL <- exp(coef(MID_Full_Log))
dwplot(ODDS_MID_FULL, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))

cplot(MID_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")

Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
ODDS_FORCE_FULL <- exp(coef(Force_Full_Log))
dwplot(ODDS_FORCE_FULL, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))

Test <- with(Mid, data.frame(US_Naval_Cap = 0:19, Relative_Cap=mean(Relative_Cap, na.rm=TRUE), Joint_Dem=mean(Joint_Dem, na.rm=TRUE), Major=mean(Major, na.rm=TRUE), Same_Region=mean(Same_Region, na.rm=TRUE), Contiguous=mean(Contiguous, na.rm=TRUE), Ally=mean(Ally, na.rm=TRUE)))

Pred_MID_LOG <- predict(m, Test, type="response", se.fit=TRUE)

margins(MID_Full_Log, at = list(US_Naval_Cap = 0:19))
cplot(MID_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")

Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
summary(Force_Full_Log2)
dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
exp(coef(Force_Full_Log2))
test1 <- data.frame(exp(coef(Force_Full_Log2)))
ggplot(exp(coef(Force_Full_Log2)))

margins(Force_Full_Log2)
cplot(Force_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of (violent)MID given US naval capabilities")

MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War, data = Master4, family=binomial)
summary(MID_Full_Log)
dwplot(MID_Full_Log)

Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
summary(Force_Full_Log)
dwplot(Force_Full_Log)

@@

##Analysis
The plot of the first set of results shows the

```{r dotwhisker_bivariate_mid, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}

dwplot(list(MID_BI_Log, MID2_BI_Log),
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) + ggtitle("test")
```

@@

```{r dotwhisker_bivariate_force, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on violent MID occurence"}

dwplot(list(Force_BI_Log, Force2_BI_Log),
        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
```

Looking

```{r dotwhisker_bivariate_force, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Full tests on MID occurence"}
dwplot(ODDS_MID_FULL, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
